---
title       : Shiny App
subtitle    : presentation
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## About the App

Shiny app contains information about the Dow Jones Industrial Average index. You
can use it to track returns and index composition.

```{r echo=FALSE}
DJIA <- dow.jan.2005[,1:6]
```

```{r}
library(portfolio)
head(DJIA)
```

--- .class #id 

## Plot

This page shows Dow Jones Industrial Average (DJIA) index returns for the chosen
period.

You can select log scale or nominal scale.

You can also select to see returns adjusted for the inflation.

--- .class #id 

## Summary

You can see more about the Down Jones Industrial averge index here.

--- .class #id 

## Table

You can see a table with the information about index components here. 
